Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-07-17 vesicle_code/docs/adhesion/adhesion.tex
fixed the shear rate notation and extension rate notation in figs and text

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a shear flow}
\label{sec:sflow} 
We consider two vesicles suspended in the shear flow $\uu = \chi(y,0)$,
where $\chi$ is the shear rate.  To be consistent with simlulations in
previous sections, the vesicles have a length of $2\pi$ for all reduced
areas.  The initial placement of the vesicles is chosen so that the flow
dives them towards one another.  In the absence of adhesion, once the
vesicles are sufficiently close, they are deflected to opposite sides of
the $y$ axis, pass one another, and then separate.  However, in the
presence of adhesion, the vesicles can form a doublet for certain values
of the separation distance $\delta$, Hamaker constant $\mathcal{H}$,
shear rate $\chi$, and reduced area $\Delta A$.  If a doublet does form,
then it undergoes a periodic motion with a period that depends on the
same parameters.

Figures~\ref{fig:doublet090-weakAdhesion}
and~\ref{fig:doublet090-strongAdhesion} show snapshots of two vesicles
that have formed a doublet and the color coding is the tension along the
vesicle.  Each of the vesicles have reduced area $\Delta A = 0.9$, shear
rate $\chi = 0.5$, separation distance $\delta = 0.4$, and Hamaker
constant $\mathcal{H} = 0.7$ (Figure~\ref{fig:doublet090-weakAdhesion})
and $\mathcal{H} = 2.1$ (Figure~\ref{fig:doublet090-strongAdhesion}).
Similar to the quiescent example, the membrane tension is negative in
the contact region indicating that the membrane is being compressed when
the adhesive force is strongest.  The two values for the Hamaker
constant are chosen since the period of the dynamics of the doublets are
both $t^* \approx 42$.  For both the Hamaker constants, the vesicles in
the doublet move in tandem with a tank-reading motion that is much
slower than the tank-treading motion that occurs in the absense of
ahdesion.  However, the dynamics of a single period for theses two
Hamaker constants differ significantly.  For the weaker adhesive force,
the individual vesicles undergo a sliding motion as they pass one
another (Figure~\ref{fig:doublet090-weakAdhesion}).  However, at larger
Hamaker constants, once the contact region is formed, the doublet
maintains the same structure and undergoes a tumbling dynamic similar to
a Jeffery orbit.

\begin{figure}[htp]
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image01.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image02.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image03.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image04.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image05.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image06.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image07.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image08.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image09.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image10.png}
  \caption{\label{fig:doublet090-weakAdhesion} The formation of a weakly
  adhered doublet in a shear flow.  The reduced area is $\Delta A =
  0.9$, the Hamaker constant is $\mathcal{H}=0.7$, the separation
  distance is $\delta = 0.4$, and the shear rate is $\chi=0.5$.  The
  interaction between the two vesicles is a sliding motion, and the
  dynamics has a period of about 42.  The color coding is the tension.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image01.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image02.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image03.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image04.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image05.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image06.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image07.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image08.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image09.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image10.png}
  \caption{\label{fig:doublet090-strongAdhesion} The formation of a
  strongly adhered doublet in a shear flow.  The reduced area is $\Delta
  A = 0.9$, the Hamaker constant is $\mathcal{H}=2.1$, the separation
  distance is $\delta = 0.4$, and the shear rate is $\chi=0.5$.  Since
  the contact region is unchanged throughout the simulation, the
  dynamics of the doublet resembles a rigid body motion with a period of
  about 42.  The color coding is the tension.}
\end{figure}

To further understand the formation of the doublet, we compute the
distance between two vesicles with reduced area $\Delta A = 0.9$,
separation distance $\delta = 0.5$, and shear rate $\chi = 0.5$.
Figure~\ref{fig:sflow_distance}(a) shows this minimum distance as a
function of time for varying Hamaker constants.  For Hamaker constants
less than a critical value, $\mathcal{H}_c$, the adhesive force is not
strong enough to form a doublet, and the distance between the vesicles
grows with time (red curves).  However, when $\mathcal{H} >
\mathcal{H}_c$, the adhesive force is sufficiently strong to bind the
vesicles into a doublet, and then the doublet undergoes a periodic
motion (blue curves).  In Figure~\ref{fig:sflow_distance}(b), we plot
the time required for the doublet to make a complete revolution for
three different shear rates and two different separation distances.
Initially, as the shear rate increases, the period decreases.  However,
the transition from the weakly adhesive doublet
(Figure~\ref{fig:doublet090-weakAdhesion}) to the stronger adhesive
doublet (Figure~\ref{fig:doublet090-strongAdhesion}) results in an
increase in the period.  Once the Hamaker constant is sufficiently
strong that the contact region remains fixed throughout the dynamics,
the period of the doublet again decreases as the shear rate increases.

Especially at the large Hamaker constants, the dynamics of the doublet
resemble those of a Jeffery orbit.  An ellipse with aspect ratio
$\lambda$ undergoes a periodic tumbling motion with
period~\cite{jef1922}
\begin{align}
  p = \frac{2\pi}{\chi}\left(\lambda + \lambda^{-1} \right).
  \label{eqn:JefferyPeriod}
\end{align}
Instead of measuring the aspect ratio of a doublet in a flow with shear
rate $\chi$, we use the computed period to define an effective aspect
ratio $\lambda_{\mathrm{eff}}$ that satisfies~\eqref{eqn:JefferyPeriod}.
Therefore, the effective aspect ratio is the aspect ratio of an ellipse
in a shear flow that is undergoing a Jeffery orbit with period $p$.  For
the Hamaker constants $\mathcal{H} = 1.5$ and $\mathcal{H} = 3.5$, the
shear rates, periods, and effective aspect ratio are summarized in
Table~\ref{tbl:aspectRatio}.  The effective aspect ratio of the doublet
depends on both the Hamaker constant and the shear rate, and this
indicates that the doublet's dynamics differ from those of a rigid body
undergoing a Jeffery orbit.

\begin{table}[htp]
\begin{minipage}{0.45\textwidth}
  $\mathcal{H} = 1.5$ \\
  \begin{tabular}{>{\centering\arraybackslash}p{2cm}
>{\centering\arraybackslash}p{2cm}
>{\centering\arraybackslash}p{2cm}}
  $\chi$ & $p$ & $\lambda_{\mathrm{eff}}$ \\
  \hline
%  0.50 & 38.06 & 2.92 \\
%  0.75 & 24.81 & 2.85 \\
%  1.00 & 19.47 & 3.00 
  0.50 & 36.34 & 2.49 \\
  0.75 & 25.86 & 2.72 \\
  1.00 & 20.73 & 2.96 
\end{tabular}
\end{minipage}
%\hfill
\begin{minipage}{0.45\textwidth}
  $\mathcal{H} = 3.5$ \\
  \begin{tabular}{>{\centering\arraybackslash}p{2cm}
>{\centering\arraybackslash}p{2cm}
>{\centering\arraybackslash}p{2cm}}
  $\chi$ & $p$ & $\lambda_{\mathrm{eff}}$ \\
  \hline
  0.50 & 28.46 & 1.66 \\
  0.75 & 22.01 & 2.17 \\
  1.00 & 17.91 & 2.44 
\end{tabular}
\end{minipage}
\caption{\label{tbl:aspectRatio} The shear rate, period, and effective
aspect ratio of a vesicle doublet with reduced area $\Delta A = 0.9$,
separation distance $\delta = 0.4$, and 
Hamaker constants $\mathcal{H} = 1.5$ and $\mathcal{H} = 3.5$.  The
effective aspect ratios depend on both the Hamaker constant and the
shear rate, indicating that for the reported Hamaker constants, the
dynamics of the doublet differ from that of a Jeffery orbit.}
\end{table}

@@

\begin{figure}
  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
  \subfigimg[width=\linewidth]{(a)}{figs/shear_adR4em1Chi5em1_ra090.pdf} &
  \subfigimg[width=\linewidth]{(b)}{figs/shear_adR4em1Chi5em1_ra090_period.pdf}
  \end{tabular}
  \caption{\label{fig:sflow_distance} (a) The distance between a pair of
  vesicles in a planar shear flow with shear rate $\chi=0.5$, and
  separation distance $\delta = 0.4$.  The different lines correspond to
  a linear spacing of Hamaker constants ranging from $\mathcal{H}=0.1$
  and $\mathcal{H}=1.0$.  (b) The time required for a doublet to
  complete a single rotation.  The reduced area is $\Delta A = 0.90$ and
  the separation distance is $\delta = 0.4$.  The different lines
  correspond to different shear rates and separation distances.}
\end{figure}

\begin{figure}
  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
  \subfigimg[width=\linewidth]{(a)}{figs/shear_adR1em1_ra090_phaseDiagram.pdf} &
  \subfigimg[width=\linewidth]{(b)}{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
  \end{tabular}
  \caption{\label{fig:sflow_phase_diagram} Phase diagram of vesicle
  hydrodynamics in a shear flow with $\delta = 0.1$ (a) and $\delta =
  0.4$ (b) with reduced area $\Delta A = 0.9$. The critical Hamaker
  constant $\mathcal{H}$ for binding of two vesicles in a shear flow
  depends on the shear rate $\chi$.  For a doublet to form, lower
  separation distances require a stronger Hamaker constants at a given
  shear rate.  The stability limit appears to be linear, indicating that
  there is potentially a stability criteria that depends on a
  dimensionless number involving the ratio of the Hamaker constant and
  shear rate.}
\end{figure}

Finally, we investigate the rheology of a suspension of a doublet by
computing the effective viscosity of a doublet and compare it to the
effective viscosity of a single tank-treading vesicle. The effective
viscosity is defined as the viscosity of a homogeneous Newtonian fluid
with the same energy dissipation per macroscopic element of fluid.  In a
simple shear flow, the intrinsic viscosity, $[\mu]$ is
\begin{align*}
  [\mu]:= \frac{\mu_{\mathrm{eff}} - \mu_0}{\phi \mu_0} = 
  \frac{1}{\chi \mu_0 (T_e - T_i)} \int_{T_i}^{T_e} 
  \langle \tau_{12} \rangle dt,
\end{align*}
where
\begin{align*}
  \langle \tau \rangle = \frac{1}{|\omega|} \int_{\gamma}
    \xxi \otimes \xx ds,
\end{align*}
$\phi$ is the area fraction of vesicles, $\tau$ is the stress due to the
vesicles, $\langle \cdot \rangle$ is the spatial average, $|\omega|$ is
the total area of both vesicles, and $\xxi$ is the traction as defined
in equation~\eqref{eqn:traction}.  In
Figure~\ref{fig:shearIntrinsicViscosity}(a), we compare the intrinsic
viscosity of a single tank-treading vesicle to a doublet with Hamaker
constant $\mathcal{H} = 0.7$, separation distance $\delta = 0.4$, and
shear rate $\chi = 0.5$.  To validate our simulations, we superimpose
(black marks) the intrinsic viscosity calculated by Ghigliotti {\em et
al.}~\cite{GhigliottiBibenMisbah2010_JFM}.  The presence of the doublet
slightly increases the intrinsic viscosity at all the reduced areas.
We also compute the intrinsic viscosity of a doublet with $\Delta A =
0.9$, $\chi = 0.5$, and $\mathcal{H} = 2.1$.  Again, this doublet has a
similar period to the case $\mathcal{H} = 0.7$. At this larger Hamaker
constant, the effective viscosity increases slightly from $1.97$ to
$2.06$.  To further characterize the effect of adhesion, in
Figure~\ref{fig:shearIntrinsicViscosity}(b) we decompose the intrinsic
viscosity into the contributions from the bending and tension (black),
and the contribution from the adhesion (green).  We also superimpose the
intrinsic viscosity of a single tank-treading vesicle (blue) to
demonstrate that the bending and tension of the doublet behave
similarly, but not identically, to a dilute suspensions of non-adhering
tank-treading vesicles.  We see that the effect of the adhesion on the
intrinsic viscosity is largest for vesicles with small reduced areas.
We also decompose the intrinsic viscosity contributions of the doublet
with $\mathcal{H} = 2.1$ and $\Delta A = 0.9$.  When compared with the
smaller Hamaker constant, the intrinsic viscosity contribution due to
bending and tension is reduced from $1.85$ to $1.71$, and the
contribution due to adhesion is increased from $0.12$ to $0.36$.
Therefore, as the Hamaker constant increases, the increase in the
intrinsic viscosity is due to the adhesive force rather than the bending
and tension.

\begin{figure}[]
  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
  \subfigimg[width=\linewidth]{(a)}{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf} &
  \subfigimg[width=\linewidth]{(b)}{figs/doublet_decomp.pdf}
  \end{tabular}
%  \centering
%  \includegraphics[width=0.45\textwidth]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
%  \includegraphics[width=0.45\textwidth]{figs/doublet_decomp.pdf}
  \caption{\label{fig:shearIntrinsicViscosity} (a) The intrinsic
  viscosity of a tank-treading vesicle (blue) and a doublet (red).  The
  shear rate is $\chi = 0.5$, the Hamaker constant is $\mathcal{H} =
  0.7$, and the separation distance is $\delta = 0.4$.  The black marks
  denote intrinsic viscosity values computed by Ghigliotti {\em et
  al.}~\cite{GhigliottiBibenMisbah2010_JFM} (cf.~Figure 5).  (b) The
  decomposition of the intrinsic viscosity into the contributions for
  the bending and tension (black) of the vesicles, and the contribution
  from the vesicle adhesion (green).  Also included is the intrinsic
  viscosity of a single tank-treading vesicle (blue).}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a shear flow}
\label{sec:sflow} 
We consider two vesicles suspended in the shear flow $\uu =
\dot\gamma(y,0)$, where $\dot\gamma$ is the shear rate.  To be
consistent with simlulations in previous sections, the vesicles have a
length of $2\pi$ for all reduced areas.  The initial placement of the
vesicles is chosen so that the flow dives them towards one another.  In
the absence of adhesion, once the vesicles are sufficiently close, they
are deflected to opposite sides of the $y$ axis, pass one another, and
then separate.  However, in the presence of adhesion, the vesicles can
form a doublet for certain values of the separation distance $\delta$,
Hamaker constant $\mathcal{H}$, shear rate $\dot\gamma$, and reduced
area $\Delta A$.  If a doublet does form, then it undergoes a periodic
motion with a period that depends on the same parameters.

Figures~\ref{fig:doublet090-weakAdhesion}
and~\ref{fig:doublet090-strongAdhesion} show snapshots of two vesicles
that have formed a doublet and the color coding is the tension along the
vesicle.  Each of the vesicles have reduced area $\Delta A = 0.9$, shear
rate $\dot\gamma = 0.5$, separation distance $\delta = 0.4$, and Hamaker
constant $\mathcal{H} = 0.7$ (Figure~\ref{fig:doublet090-weakAdhesion})
and $\mathcal{H} = 2.1$ (Figure~\ref{fig:doublet090-strongAdhesion}).
Similar to the quiescent example, the membrane tension is negative in
the contact region indicating that the membrane is being compressed when
the adhesive force is strongest.  The two values for the Hamaker
constant are chosen since the period of the dynamics of the doublets are
both $t^* \approx 42$.  For both the Hamaker constants, the vesicles in
the doublet move in tandem with a tank-reading motion that is much
slower than the tank-treading motion that occurs in the absence of
adhesion.  However, the dynamics of a single period for theses two
Hamaker constants differ significantly.  For the weaker adhesive force,
the individual vesicles undergo a sliding motion as they pass one
another (Figure~\ref{fig:doublet090-weakAdhesion}).  However, at larger
Hamaker constants, once the contact region is formed, the doublet
maintains the same structure and undergoes a tumbling dynamic similar to
a Jeffery orbit.

\begin{figure}[htp]
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image01.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image02.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image03.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image04.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image05.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image06.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image07.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image08.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image09.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image10.png}
  \caption{\label{fig:doublet090-weakAdhesion} The formation of a weakly
  adhered doublet in a shear flow.  The reduced area is $\Delta A =
  0.9$, the Hamaker constant is $\mathcal{H}=0.7$, the separation
  distance is $\delta = 0.4$, and the shear rate is $\dot\gamma=0.5$.
  The interaction between the two vesicles is a sliding motion, and the
  dynamics has a period of about 42.  The color coding is the tension.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image01.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image02.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image03.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image04.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image05.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image06.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image07.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image08.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image09.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image10.png}
  \caption{\label{fig:doublet090-strongAdhesion} The formation of a
  strongly adhered doublet in a shear flow.  The reduced area is $\Delta
  A = 0.9$, the Hamaker constant is $\mathcal{H}=2.1$, the separation
  distance is $\delta = 0.4$, and the shear rate is $\dot\gamma=0.5$.
  Since the contact region is unchanged throughout the simulation, the
  dynamics of the doublet resembles a rigid body motion with a period of
  about 42.  The color coding is the tension.}
\end{figure}

To further understand the formation of the doublet, we compute the
distance between two vesicles with reduced area $\Delta A = 0.9$,
separation distance $\delta = 0.5$, and shear rate $\dot\gamma = 0.5$.
Figure~\ref{fig:sflow_distance}(a) shows this minimum distance as a
function of time for varying Hamaker constants.  For Hamaker constants
less than a critical value, $\mathcal{H}_c$, the adhesive force is not
strong enough to form a doublet, and the distance between the vesicles
grows with time (red curves).  However, when $\mathcal{H} >
\mathcal{H}_c$, the adhesive force is sufficiently strong to bind the
vesicles into a doublet, and then the doublet undergoes a periodic
motion (blue curves).  In Figure~\ref{fig:sflow_distance}(b), we plot
the time required for the doublet to make a complete revolution for
three different shear rates and two different separation distances.
Initially, as the shear rate increases, the period decreases.  However,
the transition from the weakly adhesive doublet
(Figure~\ref{fig:doublet090-weakAdhesion}) to the stronger adhesive
doublet (Figure~\ref{fig:doublet090-strongAdhesion}) results in an
increase in the period.  Once the Hamaker constant is sufficiently
strong that the contact region remains fixed throughout the dynamics,
the period of the doublet again decreases as the shear rate increases.

Especially at the large Hamaker constants, the dynamics of the doublet
resemble those of a Jeffery orbit.  An ellipse with aspect ratio
$\lambda$ undergoes a periodic tumbling motion with
period~\cite{jef1922}
\begin{align}
  p = \frac{2\pi}{\dot\gamma}\left(\lambda + \lambda^{-1} \right).
  \label{eqn:JefferyPeriod}
\end{align}
Instead of measuring the aspect ratio of a doublet in a flow with shear
rate $\dot\gamma$, we use the computed period to define an effective
aspect ratio $\lambda_{\mathrm{eff}}$ that
satisfies~\eqref{eqn:JefferyPeriod}.  Therefore, the effective aspect
ratio is the aspect ratio of an ellipse in a shear flow that is
undergoing a Jeffery orbit with period $p$.  For the Hamaker constants
$\mathcal{H} = 1.5$ and $\mathcal{H} = 3.5$, the shear rates, periods,
and effective aspect ratio are summarized in
Table~\ref{tbl:aspectRatio}.  The effective aspect ratio of the doublet
depends on both the Hamaker constant and the shear rate, and this
indicates that the doublet's dynamics differ from those of a rigid body
undergoing a Jeffery orbit.

\begin{table}[htp]
\begin{minipage}{0.45\textwidth}
  $\mathcal{H} = 1.5$ \\
  \begin{tabular}{>{\centering\arraybackslash}p{2cm}
>{\centering\arraybackslash}p{2cm}
>{\centering\arraybackslash}p{2cm}}
  $\dot\gamma$ & $p$ & $\lambda_{\mathrm{eff}}$ \\
  \hline
%  0.50 & 38.06 & 2.92 \\
%  0.75 & 24.81 & 2.85 \\
%  1.00 & 19.47 & 3.00 
  0.50 & 36.34 & 2.49 \\
  0.75 & 25.86 & 2.72 \\
  1.00 & 20.73 & 2.96 
\end{tabular}
\end{minipage}
%\hfill
\begin{minipage}{0.45\textwidth}
  $\mathcal{H} = 3.5$ \\
  \begin{tabular}{>{\centering\arraybackslash}p{2cm}
>{\centering\arraybackslash}p{2cm}
>{\centering\arraybackslash}p{2cm}}
  $\dot\gamma$ & $p$ & $\lambda_{\mathrm{eff}}$ \\
  \hline
  0.50 & 28.46 & 1.66 \\
  0.75 & 22.01 & 2.17 \\
  1.00 & 17.91 & 2.44 
\end{tabular}
\end{minipage}
\caption{\label{tbl:aspectRatio} The shear rate, period, and effective
aspect ratio of a vesicle doublet with reduced area $\Delta A = 0.9$,
separation distance $\delta = 0.4$, and 
Hamaker constants $\mathcal{H} = 1.5$ and $\mathcal{H} = 3.5$.  The
effective aspect ratios depend on both the Hamaker constant and the
shear rate, indicating that for the reported Hamaker constants, the
dynamics of the doublet differ from that of a Jeffery orbit.}
\end{table}

@@

\begin{figure}
  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
  \subfigimg[width=\linewidth]{(a)}{figs/shear_adR4em1Chi5em1_ra090.pdf} &
  \subfigimg[width=\linewidth]{(b)}{figs/shear_adR4em1Chi5em1_ra090_period.pdf}
  \end{tabular}
  \caption{\label{fig:sflow_distance} (a) The distance between a pair of
  vesicles in a planar shear flow with shear rate $\dot\gamma=0.5$, and
  separation distance $\delta = 0.4$.  The different lines correspond to
  a linear spacing of Hamaker constants ranging from $\mathcal{H}=0.1$
  and $\mathcal{H}=1.0$.  (b) The time required for a doublet to
  complete a single rotation.  The reduced area is $\Delta A = 0.90$ and
  the separation distance is $\delta = 0.4$.  The different lines
  correspond to different shear rates and separation distances.}
\end{figure}

\begin{figure}
  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
  \subfigimg[width=\linewidth]{(a)}{figs/shear_adR1em1_ra090_phaseDiagram.pdf} &
  \subfigimg[width=\linewidth]{(b)}{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
  \end{tabular}
  \caption{\label{fig:sflow_phase_diagram} Phase diagram of vesicle
  hydrodynamics in a shear flow with $\delta = 0.1$ (a) and $\delta =
  0.4$ (b) with reduced area $\Delta A = 0.9$. The critical Hamaker
  constant $\mathcal{H}$ for binding of two vesicles in a shear flow
  depends on the shear rate $\dot\gamma$.  For a doublet to form, lower
  separation distances require a stronger Hamaker constants at a given
  shear rate.  The stability limit appears to be linear, indicating that
  there is potentially a stability criteria that depends on a
  dimensionless number involving the ratio of the Hamaker constant and
  shear rate.}
\end{figure}

Finally, we investigate the rheology of a suspension of a doublet by
computing the effective viscosity of a doublet and compare it to the
effective viscosity of a single tank-treading vesicle. The effective
viscosity is defined as the viscosity of a homogeneous Newtonian fluid
with the same energy dissipation per macroscopic element of fluid.  In a
simple shear flow, the intrinsic viscosity, $[\mu]$ is
\begin{align*}
  [\mu]:= \frac{\mu_{\mathrm{eff}} - \mu_0}{\phi \mu_0} = 
  \frac{1}{\dot\gamma \mu_0 (T_e - T_i)} \int_{T_i}^{T_e} 
  \langle \tau_{12} \rangle dt,
\end{align*}
where
\begin{align*}
  \langle \tau \rangle = \frac{1}{|\omega|} \int_{\gamma}
    \xxi \otimes \xx ds,
\end{align*}
$\phi$ is the area fraction of vesicles, $\tau$ is the stress due to the
vesicles, $\langle \cdot \rangle$ is the spatial average, $|\omega|$ is
the total area of both vesicles, and $\xxi$ is the traction as defined
in equation~\eqref{eqn:traction}.  In
Figure~\ref{fig:shearIntrinsicViscosity}(a), we compare the intrinsic
viscosity of a single tank-treading vesicle to a doublet with Hamaker
constant $\mathcal{H} = 0.7$, separation distance $\delta = 0.4$, and
shear rate $\dot\gamma = 0.5$.  To validate our simulations, we
superimpose (black marks) the intrinsic viscosity calculated by
Ghigliotti {\em et al.}~\cite{GhigliottiBibenMisbah2010_JFM}.  The
presence of the doublet slightly increases the intrinsic viscosity at
all the reduced areas.  We also compute the intrinsic viscosity of a
doublet with $\Delta A = 0.9$, $\dot\gamma = 0.5$, and $\mathcal{H} =
2.1$.  Again, this doublet has a similar period to the case $\mathcal{H}
= 0.7$. At this larger Hamaker constant, the effective viscosity
increases slightly from $1.97$ to $2.06$.  To further characterize the
effect of adhesion, in Figure~\ref{fig:shearIntrinsicViscosity}(b) we
decompose the intrinsic viscosity into the contributions from the
bending and tension (black), and the contribution from the adhesion
(green).  We also superimpose the intrinsic viscosity of a single
tank-treading vesicle (blue) to demonstrate that the bending and tension
of the doublet behave similarly, but not identically, to a dilute
suspensions of non-adhering tank-treading vesicles.  We see that the
effect of the adhesion on the intrinsic viscosity is largest for
vesicles with small reduced areas.  We also decompose the intrinsic
viscosity contributions of the doublet with $\mathcal{H} = 2.1$ and
$\Delta A = 0.9$.  When compared with the smaller Hamaker constant, the
intrinsic viscosity contribution due to bending and tension is reduced
from $1.85$ to $1.71$, and the contribution due to adhesion is increased
from $0.12$ to $0.36$.  Therefore, as the Hamaker constant increases,
the increase in the intrinsic viscosity is due to the adhesive force
rather than the bending and tension.

\begin{figure}[]
  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
  \subfigimg[width=\linewidth]{(a)}{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf} &
  \subfigimg[width=\linewidth]{(b)}{figs/doublet_decomp.pdf}
  \end{tabular}
%  \centering
%  \includegraphics[width=0.45\textwidth]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
%  \includegraphics[width=0.45\textwidth]{figs/doublet_decomp.pdf}
  \caption{\label{fig:shearIntrinsicViscosity} (a) The intrinsic
  viscosity of a tank-treading vesicle (blue) and a doublet (red).  The
  shear rate is $\dot\gamma = 0.5$, the Hamaker constant is $\mathcal{H}
  = 0.7$, and the separation distance is $\delta = 0.4$.  The black
  marks denote intrinsic viscosity values computed by Ghigliotti {\em et
  al.}~\cite{GhigliottiBibenMisbah2010_JFM} (cf.~Figure 5).  (b) The
  decomposition of the intrinsic viscosity into the contributions for
  the bending and tension (black) of the vesicles, and the contribution
  from the vesicle adhesion (green).  Also included is the intrinsic
  viscosity of a single tank-treading vesicle (blue).}
\end{figure}
